---
title: 'STOR 455 Homework #4'
subtitle: 40 points - Due  on 3/4 at 5:00pm
geometry: margin = 0.9in
output:
  word_document: default
  html_notebook: default
  pdf_document: default
---

__Situation:__ Suppose that (again) you are interested in purchasing a used vehicle. How much should you expect to pay?  Obviously the price will depend on the type of vehicle you get (the model) and how much it's been used. For this assignment you will investigate how the price might depend on the Year and mileage, as well as the state where the vehicle is purchased.  
 
__Data Source:__ To get a sample of vehicles, begin with the UsedCars CSV file. The data was acquired by scraping TrueCar.com for used vehicle listings on 9/24/2017 and contains more than 1.2 million used vehicles. For this assignment you should choose the same vehicle _Model_ from North Carolina that you initially chose for homework #2.

__Directions:__ The code below can again be used to select data from a particular _Model_ of your choice from North Carolina. The R chunk below begins with {r, eval=FALSE}. eval=FALSE makes these chunks not run when I knit the file. Before you run this chunk, you should revert it to {r}. 

```{r}
library(readr)
UsedCars <- read_csv("UsedCars.csv")

# Delete the *** below and enter the model from homework #2
ModelOfMyChoice = "EdgeSEL"
StateOfMyChoice = "NC"

# Takes a subset of your model vehicle from your state
MyVehicles = subset(UsedCars, Model==ModelOfMyChoice & State==StateOfMyChoice)
```

#### MODEL #4: Use Year and Miles as predictors for Price ####

1. Construct a model using two predictors (_Year_ and _Mileage_) with _Price_ as the response variable and provide the summary output.
```{r}
mod4=lm(Price~Year+Mileage,data=MyVehicles)
summary(mod4)
```

2. Assess the importance of each of the predictors in the regression model - be sure to indicate the specific value(s) from the summary output you are using to make the assessments. Include hypotheses and conclusions in context.
(1)For the predictor 'Year'
H0: β1=0, Ha:β1≠0
The null hypothesis is that the slope is 0, a horizontal line, a constant.The predictor year and the response price have no relationship.
Since its P value is pretty small(<2e-16), we have evidence to show that price and year have linearity relationship.It is unlikely this would happen by chance if there is no relationship with the population.
(2)For the predictor 'Mileage'
H0: β2=0, Ha:β2≠0
The null hypothesis is that the slope is 0, a horizontal line, a constant.The predictor Mileage and the response price have no relationship.
Since its P value is pretty small(<2e-16), we have evidence to show that price and Mileage have linearity relationship.It is unlikely this would happen by chance if there is no relationship with the population.

3. Assess the overall effectiveness of this model (with a formal test). Again, be sure to include hypotheses and the specific value(s) you are using from the summary output to reach a conclusion.
H0: β1=β2=0, Ha:some βi≠0
The null hypothesis is that all the slope are 0. All predictors (year and Mileage) have no relationship with the response price. The alternative hypothesis is that at least one slope is not zero.
Since the overall P value is pretty small(<2e-16), we have evidence to show that price and predictors have linearity relationship. It is unlikely this would happen by chance if there is no relationship with the population.
```{r}
source("https://raw.githubusercontent.com/JA-McLean/STOR455/master/scripts/anova455.R")
anova455(mod4)
```

4. Compute and interpret the variance inflation factor (VIF) for your predictors.
Since both of the VIF of predictors are less than 5, there is no multicollinearity problem.
```{r}
library(car)
vif(mod4)
```

5. Suppose that you are interested in purchasing a vehicle of this model that was four years old (in 2017) with 58K miles. Determine each of the following: a 90% confidence interval for the mean price at this Year and mileage,  and a 90% prediction interval for the price of an individual vehicle at this Year and mileage. Write sentences that carefully interpret each of the intervals (in terms of vehicle prices)
(1) With 90% confidence I predict that the price of a four years old EdgeSEL with 58K miles sold in NC is between $14596.97 and $22249.95
(2) With 90% confidence I predict that the mean price of a four years old EdgeSEL with 58K miles sold in NC is between $18264.54 and $18582.38
```{r}
newx=data.frame(Year=2013, Mileage=58000)
predict.lm(mod4, newx, interval="prediction",level=0.9)
predict.lm(mod4, newx, interval="confidence",level=0.9)
```

#### MODEL #5: Now Include a Categorical predictor ####    
    
For this section you will combine both datasets used in Homework #2, as well as two new datasets. Each dataset from Homework #2 included vehicles from your specific _Model_, but from two different states. You should use the same code that you used in homework #2 to construct this second dataframe with vehicles from the state of your choice, and a third and fourth dataframe with vehicles of your model from a third and fourth state (Choose either Arizona, Florida, or Ohio for the two additional states). Then manipulate the code below to combine the four dataframes into one dataframe. The R chunk below begins with {r, eval=FALSE}. eval=FALSE makes these chunks not run when I knit the file. Before you run this chunk, you should revert it to {r}.

```{r}
State1 = MyVehicles
#fill in with the dataframe of cars of your model from state 2
StateOfMyChoice2 = "PA"
State2 = subset(UsedCars, Model==ModelOfMyChoice & State==StateOfMyChoice2)
#fill in with the dataframe of cars of your model from state 3
StateOfMyChoice3 = "AZ"
State3 = subset(UsedCars, Model==ModelOfMyChoice & State==StateOfMyChoice3)
#fill in with the dataframe of cars of your model from state 4
StateOfMyChoice4 = "FL"
State4 = subset(UsedCars, Model==ModelOfMyChoice & State==StateOfMyChoice4)
# rbind combines the rows in one dataframe, assuming that the columns are the same.
CombinedStates = rbind(State1, State2, State3, State4)
```

6. Fit a multiple regression model using _Year_, _Mileage_, and _State_ to predict the _Price_ of  the vehicle. 
```{r}
mod5=lm(Price~Year+Mileage+State,data=CombinedStates)
summary(mod5)
```

7. Perform a hypothesis test to determine the importance of terms involving _State_ in the model constructed in question 6. List your hypotheses, p-value, and conclusion.
Price=β0+β1Year+β2Mileage+β3StateFL+β4StateNC+β5StateNC+β6StatePA+ε
H0: β3=β4=β5=β6=0  Ha:some βi≠0
The null hypothesis is that the slopes of States are 0. The predictor State and the response price have no relationship.
Since its P value is pretty small(9.584e-09), we have evidence to say that lines of mod4 and mod5 are different. We want to use the State term in our model because extra variability is explained by State.
```{r}
mod4=lm(Price~Year+Mileage,data=CombinedStates)
anova(mod4, mod5)
```

8. Fit a multiple regression model using _Year_, _Mileage_, _State_, and the interactions between _Year_ and _State_, and _Mileage_ and _State_ to predict the _Price_ of  the vehicle.
```{r}
mod5int=lm(Price ~ Year + State + Year*State + Mileage*State, data=CombinedStates)
summary(mod5int)
```

9. Perform a hypothesis test to determine the importance of the terms involving _State_ in the model constructed in question 8. List your hypotheses, p-value, and conclusion.
Price=β0+β1Year+...+βiMileage*State+ε
H0: β3=β4=...=0  Ha:some βi≠0
The null hypothesis is that the slopes of States are 0. The predictor State and the response price have no relationship.
Since its P value is pretty small(1.793e-09), we have evidence to say that lines of mod4 and mod5int are different. We want to use the State term in our model because extra variability is explained by State.
```{r}
mod4=lm(Price~Year+Mileage,data=CombinedStates)
anova(mod4, mod5int)
```

#### MODEL #6: Polynomial models ####
One of the drawbacks of the linear model in homework #2 was the “free vehicle” phenomenon where the predicted price is eventually negative as the line decreases for older vehicles. Let’s see if adding one or more polynomial terms might help with this. For this section you should use the dataset with vehicles from four states that you used for model 5.

10. Fit a quadratic model using _Year_ to predict _Price_ and examine the residuals. Construct a scatterplot of the data with the quadratic fit included. You should discuss each of the conditions for the linear model.
(1)linearity is fine because the red line seems to be roughly horizontal at zero for the residuals.
(2)Constant variance seems to be roughly met. From the residuals vs fitted values plot we can see a similar spread above/below the red curve for all fitted values. The variability from the line does not follow any pattern as value of the predictor changes.
(3)Normality of residuals seems to be roughly met since the data in the qqplot roughly fit the qqline. There are some deviations at each of the tails of the plot, showing some skewness of possible concern given the larger sample size of the data.
```{r}
mod6 = lm(Price~ Year+ I(Year^2), data=CombinedStates)
plot(mod6)

plot(Price~ Year, data=CombinedStates)
B0_mod6 = summary(mod6)$coef[1,1]
B1_mod6 = summary(mod6)$coef[2,1]
B2_mod6 = summary(mod6)$coef[3,1]
curve(B0_mod6 + B1_mod6*x + B2_mod6*x^2, add=TRUE)
```

11. Perform a hypothesis test to determine if any of the coefficients in this model have nonzero coefficients. List your hypotheses, p-value, and conclusion.
Assuming that adding predictors can not significantly explain variability. 
From the first line of summary, we know that P value is small so compared with the null model, adding Year can significantly explain some variability.
From the second line of summary, we know that P value is small so compared with the single linear model, adding Year^2 can significantly explain some variability.
```{r}
anova(mod6)
```

12. You are looking at a vehicle that was 4 years old (in 2017) of your model and want to find an interval that is likely to contain its _Price_ using your quadratic model. Construct an interval to predict the value of this vehicle, and include an interpretive sentence in context. 
With 95% confidence I predict that the price of a four years old EdgeSEL sold in the four states is between $12506 and $23048.51
```{r}
newxqua=data.frame(Year=2013)
predict.lm(mod6, newxqua, interval="prediction",level=0.95)
```

13. Does the quadratic model allow for some _Year_ where a vehicle has a zero or negative predicted price? Justify your answer using a calculation or graph.
No it does not. By using the discriminant for quadratic equations, which is Δ=b^2-4ac, we know that β2>0 and Δ=-5097379<0, so there is no roots in this equation and the parabola is above abscissa.
```{r}
B1_mod6^2-4*B2_mod6*B0_mod6
plot(Price~ Year, data=CombinedStates, xlim=c(1990,2020))
curve(B0_mod6 + B1_mod6*x + B2_mod6*x^2, add=TRUE)
```

14. Would the fit improve significantly if you also included a cubic term? Does expanding your polynomial model to use a quartic term make significant improvements? Justify your answer.
There is a multicollinearity issue so adding the cubic term does not create a better model. VIF test shows that there are aliased coefficients in the model. 
```{r}
mod6cub = lm(Price~ Year+I(Year^2)+I(Year^3), data=CombinedStates)
summary(mod6cub)
vif(mod6cub)
```
```{r}
year_bar=mean(CombinedStates$Year)
mod6cubbar = lm(Price~ Year+I((Year-year_bar)^2)+I((Year-year_bar)^3), data=CombinedStates)
summary(mod6cubbar)
```


#### MODEL #7: Complete second order model ####
For this section you should again use the dataset with vehicles from four states that you used for models 5 and 6.

15.	Fit a complete second order model for predicting a used vehicle _Price_ based on _Year_ and _Mileage_ and examine the residuals. You should discuss each of the conditions for the linear model.
(1)linearity is fine because the red line seems to be roughly horizontal at zero for the residuals.
(2)Constant variance seems to be roughly met. From the residuals vs fitted values plot we can see a similar spread above/below the red curve for all fitted values.
(3)Normality of residuals seems to be roughly met since the data in the qqplot roughly fit the qqline. There are some deviations at each of the tails of the plot, showing some skewness of possible concern given the larger sample size of the data.
```{r}
mod7=lm(Price~Year+Mileage+I(Year^2)+I(Mileage^2)+I(Year*Mileage),data=CombinedStates)
summary(mod7)
plot(mod7)
```

16. Perform a hypothesis test to determine if any of the coefficients in this model have nonzero coefficients. List your hypotheses, p-value, and conclusion.
Assuming all of those coefficients are zero while the alternative is that in those coefficients at least one of them is non zero. P value is big(0.3244) so we should not use the full second order. 
```{r}
mod7_reduced1=lm(Price~Year+Mileage+I(Year^2)+I(Mileage^2),data=CombinedStates)
anova(mod7_reduced1,mod7)
```

17. Perform a hypothesis test to determine the importance of just the second order terms (quadratic and interaction) in the model constructed in question 15. List your hypotheses, p-value, and conclusion.
Assuming that the second order terms can not significantly explain extra variability. P value is small so it make sense to keep those second order terms.
```{r}
mod7_reduced2=lm(Price~Year+Mileage,data=CombinedStates)
anova(mod7_reduced2,mod7)
```

18. Perform a hypothesis test to determine the importance of just the terms that involve _Mileage_ in the model constructed in question 15. List your hypotheses, p-value, and conclusion.
Assuming that the year term can not significantly explain more variability. P value is small so it make sense to keep the year term.
```{r}
mod7_reduced3=lm(Price~Mileage+I(Mileage^2),data=CombinedStates)
anova(mod7_reduced3,mod7)
```

