---
title: "STOR 455 Homework 7"
subtitle: 25 points - Due Friday 4/1 9:00am
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
---

### Are Emily and Greg More Employable Than Lakisha and Jamal? ###

Bertrand, M., & Mullainathan, S. (2004). Are Emily and Greg more employable than Lakisha and Jamal? A field experiment on labor market discrimination. _American Economic Review, 94_(4), pp. 991-1013.

\[Abstract\]
We perform a field experiment to measure racial discrimination in the labor market. We respond with fictitious resumes to help-wanted ads in Boston and Chicago newspapers. To manipulate perception of race, each resume is randomly assigned either a very African American sounding name or a very White sounding name. The results show significant discrimination against African-American names: White names receive 50 percent more callbacks for interviews. We also find that race affects the benefits of a better resume. For White names, a higher quality resume elicits 30 percent more callbacks whereas for African Americans, it elicits a far smaller increase. Applicants living in better neighborhoods receive more callbacks but, interestingly, this effect does not differ by race. The amount of discrimination is uniform across occupations and industries. Federal contractors and employers who list “Equal Opportunity Employer” in their ad discriminate as much as other employers. We find little evidence that our results are driven by employers inferring something other than race, such as social class, from the names. These results suggest that racial discrimination is still a prominent feature of the labor market.    


Variables     | Descriptions
-----------   | -----------------------------------------------------
_call_        | Was the applicant called back? (1 = yes; 0 = no)
_ethnicity_   | indicating ethnicity (i.e., "Caucasian-sounding" vs. "African-American sounding" first name)
_sex_         | indicating sex
_quality_     | Indicating quality of resume.
_experience_  | Number of years of work experience on the resume
_equal_       | Is the employer EOE (equal opportunity employment)?


Use the _ResumeNames455_ found at the address below:

https://raw.githubusercontent.com/JA-McLean/STOR455/master/data/ResumeNames455.csv
```{r}
library(readr)
ResumeNames455 <- read_csv("https://raw.githubusercontent.com/JA-McLean/STOR455/master/data/ResumeNames455.csv") 
```

1) An Equal Opportunity Employer (EOE) is an employer who agrees not to discriminate against any employee or job applicant because of race, color, religion, national origin, sex, physical or mental disability, or age. Construct a logistic model to predict if the job applicant was called back using _ethnicity_, _equal_, _sex_, and the interactions between _ethnicity_ and _equal_, and _sex_ and _equal_ as the predictor variables. 
```{r}
mod=glm(call~ethnicity+sex+equal+ethnicity*equal+sex*equal,family = binomial, data=ResumeNames455)
summary(mod)
```

2)  Conduct a drop in deviance hypothesis test to determine the effectiveness of the _equal_ terms in the model constructed in the previous question. Cite your hypotheses, p-value, and conclusion in context.
H0:β3=0 Ha:β3≠0
We cannot reject H0(p-value=0.2629), the equal term cannot significantly improve the model.
```{r}
mod2=glm(call~ethnicity+sex,family = binomial, data=ResumeNames455)
anova(mod2, mod, test="Chisq")
1 - pchisq(summary(mod2)$deviance - summary(mod)$deviance, 3)
```

3)  Based on your model from question 1, What is the probability of a male applicant with a "Caucasian-sounding" name getting a call back from an Equal Opportunity Employer (EOE)? What is the probability of a female applicant with an "African-American sounding" name getting a call back from an Equal Opportunity Employer (EOE)?
```{r}
person1=data.frame(sex='male',ethnicity='cauc',equal='yes')
person2=data.frame(sex='female',ethnicity='afam',equal='yes')
predict(mod,person1, type = "response")
predict(mod,person2, type = "response")
```

4) Does the number of years of work experience impact the relationship between _ethnicity_, _sex_, and an applicant getting called back? Construct a logistic model to predict if the job applicant was called back using _ethnicity_, _sex_, _experience_, and the interactions between _ethnicity_ and _experience_, and _sex_ and _experience_ as the predictor variables. 
```{r}
mod3=glm(call~ethnicity+sex+experience+ethnicity*experience+sex*experience,family = binomial, data=ResumeNames455)
summary(mod3)
```

5)  Conduct a drop in deviance hypothesis test to determine the effectiveness of the _experience_ terms in the model constructed in the previous question. Cite your hypotheses, p-value, and conclusion in context.
H0:β3=0 Ha:β3≠0
We can reject H0(p-value=4.958e-05), The experience term can significantly improve the model.
```{r}
anova(mod2, mod3, test="Chisq")
1 - pchisq(summary(mod2)$deviance - summary(mod3)$deviance, 3)
```

6)  Construct a plot with _experience_ on the horizontal axis and _call_ on the vertical axis. Add to this plot four curves, made from the model constructed in question 4. Comment on the similarities or differences between the four curves.
    *   For an male applicant with a "Caucasian-sounding" name, add to the plot a red logistic curve showing the probability of getting a call back based on experience. 
    *   For an female applicant with a "Caucasian-sounding" name, add to the plot a green logistic curve showing the probability of getting a call back based on experience.
    *   For a male applicant with an "African-American sounding" name, add to the plot a blue logistic curve showing the probability of getting a call back based on experience.
    *   For a female applicant with an "African-American sounding" name, add to the plot a orange logistic curve showing the probability of getting a call back based on experience. 
The curve of both female is trending upward and the curve of both male has a flatting trend, which means that female with more years of experience are more likely to be calling back while to male years of experience has no obvious influence.
caucasian male applicants have higher calling back rate compared with african american male applicants.
caucasian female applicants also have higher calling back rate compared with african american female applicants.
Overall caucasian applicants have higher calling back rate.
```{r}
logit = function(B0, B1, x)
  {exp(B0+B1*x)/(1+exp(B0+B1*x))}

plot(call~experience,data=ResumeNames455)

B0 = summary(mod3)$coef[1]
B1 = summary(mod3)$coef[2]
B2 = summary(mod3)$coef[3]
B3 = summary(mod3)$coef[4]
B4 = summary(mod3)$coef[5]
B5 = summary(mod3)$coef[6]
curve(exp(B0+B1+B2+(B3+B4+B5)*x)/(1+exp(B0+B1+B2+(B3+B4+B5)*x)),
                                  add=TRUE, col="red")
curve(exp(B0+B1+(B3+B4)*x)/(1+exp(B0+B1+(B3+B4)*x)),
                                  add=TRUE, col="green")
curve(exp(B0+B2+(B3+B5)*x)/(1+exp(B0+B2+(B3+B5)*x)),
                                  add=TRUE, col="blue")
curve(exp(B0+B3*x)/(1+exp(B0+B3*x)),
                                  add=TRUE, col="orange")
```

7)  Use an appropriate model selection method to construct a best model to predict if the job applicant was called back using any of the variables as predictors (except for _name_). You may also use interaction terms. Why would you not want to use _name_ as a predictor?
Different people have different name. There is no significant features or patterns in the words of people's names. The name can only represent that people themselves.
```{r}
library(MASS)
ResumeNames455.1 = within(ResumeNames455, 
                     {name = NULL})

fullmod = glm(call~., data=ResumeNames455.1, family="binomial")
final_model_backwards=stepAIC(fullmod, trace=FALSE) 
summary(final_model_backwards)
```
