---
title: 'Homework #3: Ames Housing Data'
subtitle: 40 points - Due 2/21 at 5:00pm
output:
  html_notebook: 
    toc: yes
    toc_float: yes
    highlight: espresso
    theme: readable
---

_Situation_: Can we predict the selling price of a house in Ames, Iowa based on recorded features of the
house? That is your task for this assignment. Each group will have a dataset with information on forty
potential predictors and the selling price (in $1,000’s) for a sample of homes. The data set for your group
is in AmesTrain??.csv (where ?? corresponds to your group number) and can be found in the AmesTrain
zipped file under class 14 in Sakai. A separate file identifies the variables in the Ames Housing data and
explains some of the coding.

_Directions_: You will be assigned to a group of three to four students for this assignment. Parts 1, 2, &
5 should be turned in individually to Gradescope by each student in your group. Parts 3 & 4 should be
submitted as a group to Gradescope. There are separate places to submit the individual and group portions
of the assignment.

```{r results='hide'}
library(readr)
library(car)
library(carData)
library(corrplot) 
library(leaps) 

AmesTrain15 <- read_csv('AmesTrain15.csv')

source("https://raw.githubusercontent.com/JA-McLean/STOR455/master/scripts/ShowSubsets.R")
```

# Part 1. Build an initial "basic" model
mod1: the linear relationship is overall good.
The P value of some predictors are large, which are not good for being predictors or because of multicollinearity.
The VIF of some variables are lager than 5.
```{r}
library(dplyr)
#remove the categorical variables
newdata=select_if(AmesTrain15,is.numeric)
#remove the Order variable and predictors that are exactly related
newdata1=subset(newdata,select =-c(Order,BasementSF,GroundSF))

mod1 = lm(Price~., data=newdata1)
plot(mod1)
summary(mod1)
vif(mod1)
```

## backward method
```{r}
MSE = (summary(mod1)$sigma)^2
backward_mod = step(mod1, scale=MSE,trace=FALSE)
summary(backward_mod)
```
## stepwise method
Both of the backward and stepwise methods have the same adjusted R square.
Compared with mod1, the model improves from 0.8588 to 0.8595.
The predictor of 'Bedroom' and 'Fireplaces' have p values greater than 0.05, which are not significant at a 5% level.
There is no multicollinearity, all VIF is smaller than 5.
I choose it as my basic model.
```{r}
none = lm(Price~1, data=newdata1)
stepwise_mod = step(none, scope=list(upper=mod1), scale=MSE,trace=FALSE)
summary(stepwise_mod)
vif(stepwise_mod)
```
# Part 2: Residual analysis
Linearity is ok, since the residuals vs fitted plot is described by a horizontal line.\
qq plot: a little bit of a compacted on both sides of this because the ends points go down below the line a little bit.\
But overall, it is good without clearly huge skews.
The 12 houses indexes listed are outliers, they have studentized residuals larger than 3 or or smaller than -3.\
All cook's distance are smaller than 0.5, so there is no data points have a drastic effect on the whole model.
Overall, the result of residual analysis is good.\
I made an adjustment based on P value above, which deletes the predictor of 'Bedroom' and 'Fireplaces', the adjusted R is smaller, which is 0.8582.
```{r}
plot(stepwise_mod)
head(sort(abs(rstudent(stepwise_mod)), decreasing=TRUE), 15)
head(sort(cooks.distance(stepwise_mod), decreasing=TRUE), n=5)

adjustmod = lm(formula = Price ~ Quality + FirstSF + SecondSF + YearBuilt + 
    BasementFinSF + GarageSF + LotArea + YearRemodel + Condition + 
    ScreenPorchSF + LotFrontage + BasementUnFinSF + EnclosedPorchSF, data = newdata1)
summary(adjustmod)
```

# Part 3 & 4: Group work
# Part 5: Final model
(The fancier final model is put in group work.) A 95% prediction interval for the Price of this house is (228.7178, 348.0183).
```{r}
newHouse=data.frame(LotFrontage=400,
LotArea=21540,
Quality=7,
Condition=5,
YearBuilt=1983,
YearRemodel=1999,
BasementUnFinSF=757,
BasementFinSF=0,
BasementSF=757,
FirstSF=1485,
SecondSF=947,
BasementFBath=0,
Bedroom=4,
Fireplaces=1,
GarageCars=2,
GarageSF=588,
EnclosedPorchSF=0,
ScreenPorchSF=0)

predict.lm(stepwise_mod, newHouse, interval="prediction")
```

3.2 class 22 cross validation
```{r}
set.seed(12345)
rows <- sample(nrow(newdata1))
Price_shuffled = newdata1[rows,]

PriceTrain=Price_shuffled[1:480,]      
PriceHoldout=Price_shuffled[481:600,]   
```

```{r}
fitprice=predict(stepwise_mod,newdata=PriceHoldout)
fitprice
holdoutresid=PriceHoldout$Price - fitprice
holdoutresid
```

1.in hold out set the mean is 2.001697,which is close to zero since the price is thousands of dollars.\
2.the std is also close.\
3.the normality is similar. Both of the tails in hold out sample and the training sample are fall from the line.
```{r}
mean(holdoutresid)
mean(stepwise_mod$resid)

sd(holdoutresid)
summary(stepwise_mod)$sigma

qqnorm(holdoutresid)
qqline(holdoutresid)
plot(stepwise_mod,2)
```

```{r}
crosscorr=cor(PriceHoldout$Price,fitprice)
crosscorr
crosscorr=cor(PriceHoldout$Price,fitprice)^2
shrinkage = summary(stepwise_mod)$r.squared-crosscorr^2
shrinkage
```
